What's hot and what's not:\\Windowed developer topic analysis

### 2009-04-12 lda-paper.tex
Removed some indefinites

The \emph{trend-time-line} (Figure
\ref{fig:trendtimeline}) displays repeating trends more clearly by
dedicating a horizontal line for trend segments belonging to one
trend. This means that if a trend contains discontinuous segments then
the segments appear on the same line.  However, the least common
trends need to be pruned away or the view will be very long.

@@

Previous work on topic analysis that employed LSI and LDA typically
extracted a specified number of topics and then tracked them over
time. This means that a single, static set of topics was tracked
across the whole development history of a project, we refer to this as \emph{global topic
  analysis}.% is topic analysis applied against the entire lifetime of a
%project.

>>>>

The \emph{trend-time-line} (Figure
\ref{fig:trendtimeline}) displays repeating trends more clearly by
dedicating a horizontal line for trend segments belonging to one
trend. Therefore if a trend contains discontinuous segments then
the segments appear on the same line.  However, the least common
trends need to be pruned away or the view will be very long.

@@

% Previous work on topic analysis that employed LSI and LDA typically
% extracted a specified number of topics and then tracked their
% relationship to documents over time. This means that a single, static
% set of topics was tracked across the whole development history of a
% project, we refer to this as \emph{global topic
%   analysis}.% is topic analysis applied against the entire lifetime of a
% %project.

Previous work on topic analysis that employed LSI and LDA typically
extracted a specified number of topics from the entire development
history of a project and then tracked their relationships to documents
over time, we call this \emph{global topic analysis}.

% This means that a single, static
%set of topics was tracked across the whole development history of a
%project, we refer to this as \emph{global topic
%  analysis}.% is topic analysis applied against the entire lifetime of a
%project.
